On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-05 Manuscript/manuscript.tex
Clopper-Pearson in reply and Manuscript

The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the number of replicates. Then
$cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$, for
$r \in \{1, \ldots, R\}$. If a CI method is valid, then the coverage rate is
expected to match the nominal level. Because it is unlikely for the coverage to 
exactly match the nominal level, we can construct a 95\% Wald-type CI of the 
coverage rate 
(which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
is included in the interval, the block bootstrap method is likely performing 
well. If all values in the interval are below 0.95, the results would suggest 
that the method either is providing inaccurate estimation, is underestimating 
the process' variability, or a combination of both. If all values in the 
interval are above .95, the results suggest that the method is overestimating 
the process' variability. \citet{brown2001interval} notes that the Wald-type 
interval has poor coverage as the proportion approaches 0 or 1.
\textbf{Figures~\ref{fig:mu1}--\ref{fig:phi2}} 
summarizes the empirical coverage rates and the 95\% confidence intervals of the 
real coverage for a standard normal marginal distribution, generated using the 
R \textsl{ggplot2} package.\citep{ggplot2}

@@

@@

@@

@@

>>>>

The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the number of replicates. Then
$cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$, for
$r \in \{1, \ldots, R\}$. If a CI method is valid, then the coverage rate is
expected to match the nominal level. Because it is unlikely for the coverage to 
exactly match the nominal level, we can construct a 95\% Wald-type CI of the 
coverage rate 
(which is an estimate of a proportion with $R = 10000$). If the proportion 0.95 
is included in the interval, the block bootstrap method is likely performing 
well. If all values in the interval are below 0.95, the results would suggest 
that the method either is providing inaccurate estimation, is underestimating 
the process' variability, or a combination of both. If all values in the 
interval are above .95, the results suggest that the method is overestimating 
the process' variability. \citet{brown2001interval} notes that the Wald-type 
interval has poor coverage as the proportion approaches 0 or 1.
\textbf{Figures~\ref{fig:mu1}--\ref{fig:phi1}} 
summarizes the empirical coverage rates and the 95\% confidence intervals of the 
real coverage for a standard normal marginal distribution using block bootstrap
with $l = \lceil n^{1/3} \rceil$, generated using the 
R \textsl{ggplot2} package.\citep{ggplot2}

@@

\textbf{Figures~\ref{fig:exp_mu1}--\ref{fig:exp_phi1}} 
summarizes the empirical coverage rates and the 95\% confidence intervals of the 
real coverage for a exponential marginal distribution using block bootstrap
with $l = \lceil n^{1/3} \rceil$.

@@

CIs for $\mu$ exhibit coverage rates quite close to 1 for $\phi = -0.4$, and
as stated before, the Wald-type CI is known to have undercoverage in such 
situations.
Figure~\ref{fig:norm_mu_1_cp} shows the same coverage rates using exact 
Clopper-Pearson intervals to verify that it is the choice of Wald interval
does not cause undercoverage of the coverage rate. Indeed, the widths of the
exact proportion CIs do not seem to differ heavily from the Wald-type CIs.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1_cp}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs 
    for
    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
    error bars represent 95\% exact CIs of the real coverage rates.}
  \label{fig:norm_mu_1_cp}
\end{figure}

@@

\textbf{Figures~\ref{fig:mu2}--\ref{fig:phi2}} 
summarizes the empirical coverage rates and the 95\% confidence intervals of the 
real coverage for a standard normal marginal distribution using block bootstrap
with $l = \lceil 2n^{1/3} \rceil$.

@@

\textbf{Figures~\ref{fig:exp_mu2}--\ref{fig:exp_phi2}} 
summarizes the empirical coverage rates and the 95\% confidence intervals of the 
real coverage for a exponential marginal distribution using block bootstrap
with $l = \lceil 2n^{1/3} \rceil$.

### 2024-01-05 Manuscript/reply.tex
Clopper-Pearson in reply and Manuscript

>>>>

We have also included these comments and a figure in the Results section which 
uses exact 
Clopper-Pearson CIs:

CIs for $\mu$ exhibit coverage rates quite close to 1 for $\phi = -0.4$, and
as stated before, the Wald-type CI is known to have undercoverage in such 
situations.
Figure~\ref{fig:norm_mu_1_cp} shows the same coverage rates using exact 
Clopper-Pearson intervals to verify that it is the choice of Wald interval
does not cause undercoverage of the coverage rate. Indeed, the widths of the
exact proportion CIs do not seem to differ heavily from the Wald-type CIs.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/plot_norm_mu_1_cp}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs 
    for
    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
    error bars represent 95\% exact CIs of the real coverage rates.}
  \label{fig:norm_mu_1_cp}
\end{figure}
